GEE models

### 2017-10-02 doc/esm.Rmd
more detail about ar1/corr matrix in esm

Generalized estimating equations (GEE) is a technique similar to mixed effects 
modeling, except it calculates the marginal population estimates compared to the
subject-specific estimates in mixed effects models. GEE is well suited to and
commonly used in longitudinal cohort studies, especially given its capacity to
handle missed visits. GEE is able to handle longitudinal data due to the
estimating of a working correlation matrix, which was chosen based on
quasi-likelihood information criteria (QIC). The auto-regressive of order 1
(AR1) matrix was chosen for the GEE models as it had the best model fit accessed
using QIC, though other matrices (eg. exchangeable) had similar fit (data not
shown).

>>>>

Generalized estimating equations (GEE) is a technique similar to mixed effects 
modeling, except it calculates the marginal population estimates compared to the
subject-specific estimates in mixed effects models. GEE is well suited to and
commonly used in longitudinal cohort studies, especially given its capacity to
handle missed visits. GEE is able to handle longitudinal data due to the
estimating of a working correlation matrix, which was chosen based on
quasi-likelihood information criteria (QIC). The auto-regressive of order 1
(AR1) matrix was chosen for the GEE models as it had the best model fit accessed
using QIC, though other matrices (eg. exchangeable) had similar fit (data not
shown). One main advantage of using methods such as GEE is the inclusion of the
working correlation matrix that takes into account the inherent covariance
between values measured at different time points when computing model estimates
and standard errors. AR1 is the most appropriate correlation matrix for
longitudinal data since the correlation matrix assumes lower intercorrelation of
outcomes within an individual as time passes. For example, BMI measured at the
baseline visit would be more highly correlated to BMI measured at the 3rd year
visit than compared to the 6th year visit.
